---
title: "NZness"
author: "David Hood, IT Training and Development, University of Otago"
date: "10/5/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(cache.path = "../cache/")
```

```{r libraries}
library(rtweet)
library(dplyr, quietly = TRUE)
library(ggplot2)
library(tidyr)
library(knitr)
library(stringr)
```


```{r load_hetangata}
hetangata <- readLines("~/Syncplicity Folders/support_files/hetangata.txt")
```

```{r load_nz_by_friends, cache=TRUE}
have_data_on <- list.dirs("../fsc_acc", full.names=FALSE)
have_data_on <- have_data_on[have_data_on != ""]
# 1234567890/fav_1234567890.csv is the form for fave
# 1234567890/who_1234567890.csv is the form for profile
# 1234567890/frn_1234567890.csv is the form for friends (those followed)
favs <- paste0("../fsc_acc/", have_data_on, "/fav_", have_data_on, ".csv")
profiles <- paste0("../fsc_acc/", have_data_on, "/who_", have_data_on, ".csv")
frns <- paste0("../fsc_acc/", have_data_on, "/frn_", have_data_on, ".csv")

read_frns <- function(x) {
  if(file.exists(x)){
    filinf <- file.info(x)
    if(filinf$size < 8){
      return(NULL)
      }
    stored_frns <- read.csv(x, colClasses = "character")
    stored_frns %>%
      mutate(friends_id = gsub("x","",user_id)) %>%
      select(user, friends_id) %>%
      return()
  } else {
    return(NULL)
  }
}

frnset <- bind_rows(lapply(frns, read_frns))
frnset$kiwi <- as.numeric(frnset$friends_id %in% hetangata)
nzfriends <- frnset %>% group_by(user) %>% summarise(kwness = sum(kiwi))
rm(frnset)
```

```{r load_nz_profiles, cache=TRUE}

read_profile <- function(x) {
  if(file.exists(x)){
    filinf <- file.info(x)
    if(filinf$size < 8){
      return(NULL)
      }
    stored_prof <- read.csv(x, colClasses = "character")
      return(stored_prof)
  } else {
    return(NULL)
  }
}

profset <- bind_rows(lapply(profiles, read_profile)) #40798
profiles <- profset %>%
    select(user_id, screen_name, country_code, name, 
           location, description, account_created_at) %>% 
    mutate(user_id = gsub("x","",user_id)) 
```

Comparing NZness of friends (people followed) with profile information

```{r}
combined_data <- nzfriends %>% inner_join(profiles, by=c("user" = "user_id")) #40694
combined_data %>%
    mutate(nz_by_cc = case_when(
        country_code == "NZ" ~ "NZ",
        !is.na(country_code) ~ "other",
        TRUE ~ NA_character_
    )) %>%
    ggplot(aes(colour=nz_by_cc, x=kwness)) + geom_density()

```

As table (for key early stage)

```{r}
combined_data %>%
    mutate(nz_by_cc = case_when(
        country_code == "NZ" ~ "NZ",
        !is.na(country_code) ~ "other",
        TRUE ~ NA_character_
    )) %>%
    count(nz_by_cc,kwness) %>%
    group_by(nz_by_cc) %>%
    mutate(prop = n / sum(n, na.rm=TRUE)) %>%
    ungroup() %>%
    filter(kwness < 30) %>%
    select(-n) %>%
    spread(nz_by_cc, prop, fill=0) %>% kable()

```

Looks like following about 25  (allowing for blanks) is the crossover point for NZness

testing against macros in the description
```{r}
combined_data %>%
    mutate(macrons = (as.numeric(str_detect(tolower(description), "Ä")) +
               as.numeric(str_detect(tolower(description), "Ä“")) +
               as.numeric(str_detect(tolower(description), "Ä«")) +
               as.numeric(str_detect(tolower(description), "Å")) +
               as.numeric(str_detect(tolower(description), "Å«"))) > 0
               ) %>%
    ggplot(aes(colour=macrons, x=kwness)) + geom_density()
```

```{r}
combined_data %>%
    mutate(macrons = (as.numeric(str_detect(tolower(description), "Ä")) +
               as.numeric(str_detect(tolower(description), "Ä“")) +
               as.numeric(str_detect(tolower(description), "Ä«")) +
               as.numeric(str_detect(tolower(description), "Å")) +
               as.numeric(str_detect(tolower(description), "Å«"))) > 0
               ) %>%
    count(macrons,kwness) %>%
    group_by(macrons) %>%
    mutate(prop = n / sum(n, na.rm=TRUE)) %>%
    ungroup() %>%
    filter(kwness < 30) %>%
    select(-n) %>%
    spread(macrons, prop, fill=0) %>% kable()
```

It seems any macrons is a good measure of NZness.

Testing Self declared location:

```{r}
combined_data %>%
    mutate(desc_nz = (as.numeric(str_detect(tolower(description), "zealand")) +
               as.numeric(str_detect(tolower(description), "nz")) +
               as.numeric(str_detect(tolower(description), "n.z")) +
               as.numeric(str_detect(tolower(description), "n. z")) +
               as.numeric(str_detect(tolower(description), "n z")) +
               as.numeric(str_detect(tolower(description), "n z")) +
               as.numeric(str_detect(tolower(description), "aotearo")) +
               as.numeric(str_detect(tolower(description), "auckland")) +
               as.numeric(str_detect(tolower(description), "wellington")) +
               as.numeric(str_detect(tolower(description), "christchurch")) +
               as.numeric(str_detect(tolower(description), "dunedin")) +
               as.numeric(str_detect(tolower(description), "ðŸ‡³ðŸ‡¿"))
               ) > 0
               ) %>%
    ggplot(aes(colour=desc_nz, x=kwness)) + geom_density()
```

Not as good as other measures

Checking location

```{r}
combined_data %>%
    mutate(desc_nz = (as.numeric(str_detect(tolower(location), "zealand")) +
               as.numeric(str_detect(tolower(location), "nz")) +
               as.numeric(str_detect(tolower(location), "n.z")) +
               as.numeric(str_detect(tolower(location), "n. z")) +
               as.numeric(str_detect(tolower(location), "n z")) +
               as.numeric(str_detect(tolower(location), "n z")) +
               as.numeric(str_detect(tolower(location), "aotearo")) +
               as.numeric(str_detect(tolower(location), "auckland")) +
               as.numeric(str_detect(tolower(location), "wellington")) +
               as.numeric(str_detect(tolower(location), "christchurch")) +
               as.numeric(str_detect(tolower(location), "dunedin")) +
               as.numeric(str_detect(tolower(location), "ðŸ‡³ðŸ‡¿"))
               ) > 0
               ) %>%
    ggplot(aes(colour=desc_nz, x=kwness)) + geom_density()
```

Location better than description.

favs of NZ people

```{r load_nz_favs, cache=TRUE}

read_favs <- function(x) {
  if(file.exists(x)){
    filinf <- file.info(x)
    if(filinf$size < 8){
      return(NULL)
      }
    stored_frns <- read.csv(x, colClasses = "character")
    stored_frns %>%
      mutate(liked_id = gsub("x","",user_id)) %>%
      select(user= favorited_by, liked_id) %>%
      return()
  } else {
    return(NULL)
  }
}

favset <- bind_rows(lapply(favs, read_favs))
favset$kiwi <- as.numeric(favset$liked_id %in% hetangata)
nzfavs <- favset %>% group_by(user) %>% summarise(likekw = sum(kiwi))
rm(favset)

```


what does matching friends w. favs look like
```{r}
combined_data %>% inner_join(nzfavs, by="user") %>%
    ggplot(aes(x=kwness,y=likekw,colour=(country_code=="NZ"))) + geom_point(size=0.4) +
    facet_wrap(~(country_code=="NZ"), ncol=1) + coord_equal()
```

For location, who you follow gives better seperation than what you like.
